### 2024-06-01 player-evaluation.qmd
20240601 - incentives
20240601 - stock picking

@@

- work ethic and mental toughness
- whether they are in a contract year

>>>>

Evaluating players for fantasy football could be thought of as similar to evaluating companies when buying stocks.
You want to evaluate and compare various assets so that you get the assets with the best value.

@@

- work ethic and mental toughness
- incentives
    - contract performance incentives
    - whether they are in a contract year
